\documentclass[12pt]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{fancyhdr}
\usepackage{setspace}

\pagestyle{fancy}
\fancyhf{}
\rhead{Bobby's School System}
\lhead{Requirement Analysis}
\rfoot{\thepage}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.5em}{}

\title{\textbf{Requirement Analysis: Bobby's School System}}
\author{Glen Paul Chirayath Shaju \\ Sai Bharghav Thoomu}
\date{}

\begin{document}
\maketitle
\onehalfspacing

\section{Introduction}
This document presents a full requirement analysis for the proposed school management system for Bobby's School. It outlines what the system needs, what stakeholders want, and how these requirements can be realized.

\section{Functional Requirements}
\begin{itemize}
    \item \textbf{Student Management:} Registration, attendance tracking, performance records, promotion history.
    \item \textbf{Teacher Management:} Profiles, schedules, subjects, attendance, performance reviews.
    \item \textbf{Class Management:} Timetabling, subject allocation, classroom allocation.
    \item \textbf{Examination System:} Exam schedules, grading, report cards.
    \item \textbf{User Management:} Role-based access for Admin, Teachers, Students, and Parents.
\end{itemize}

\section{Use Cases}
\subsection*{UC1: Student Registration}
\textbf{Actors:} Student / Admin / Parent \\
\textbf{Goal:} Register a new student \\
\textbf{Flow:}
\begin{enumerate}
    \item Login and access Registration
    \item Fill in personal and academic details
    \item Submit the form
    \item System stores data and notifies Admin
\end{enumerate}

\subsection*{UC2: Attendance Tracking}
\textbf{Actors:} Teacher / Student / Parent \\
\textbf{Goal:} Mark or view attendance \\
\textbf{Flow:}
\begin{enumerate}
    \item Teacher selects class/date, marks attendance
    \item System updates records
    \item Students/Parents view attendance
\end{enumerate}

\subsection*{UC3: Performance Records}
\textbf{Actors:} Teacher / Student / Parent \\
\textbf{Goal:} Enter/view academic performance \\
\textbf{Flow:}
\begin{enumerate}
    \item Teacher enters grades
    \item System stores and validates
    \item Data visible to stakeholders
\end{enumerate}

\subsection*{UC4: Promotion History}
\textbf{Actors:} Teacher / Admin \\
\textbf{Goal:} Update/view promotion status \\
\textbf{Flow:}
\begin{enumerate}
    \item Admin updates status
    \item System saves and notifies stakeholders
\end{enumerate}

\subsection*{UC5: Teacher Profile Management}
\textbf{Actors:} Teacher / Admin \\
\textbf{Goal:} Update/view teacher profile \\
\textbf{Flow:}
\begin{enumerate}
    \item Edit and save profile details
    \item System validates and stores
\end{enumerate}

\subsection*{UC6: Schedule Management}
\textbf{Actors:} Admin \\
\textbf{Goal:} Assign teacher schedules \\
\textbf{Flow:}
\begin{enumerate}
    \item Input teacher timetable
    \item System saves and shares
\end{enumerate}

\subsection*{UC7: Subject Assignment}
\textbf{Actors:} Admin \\
\textbf{Goal:} Assign subjects to teachers \\
\textbf{Flow:}
\begin{enumerate}
    \item Admin selects teacher/subjects
    \item System confirms assignment
\end{enumerate}

\subsection*{UC8: Teacher Attendance}
\textbf{Actors:} Admin / Teacher \\
\textbf{Goal:} Monitor/record attendance \\
\textbf{Flow:}
\begin{enumerate}
    \item Admin or teacher records attendance
    \item Data is stored for HR
\end{enumerate}

\subsection*{UC9: Performance Reviews}
\textbf{Actors:} Admin / Academic Department \\
\textbf{Goal:} Evaluate teacher performance \\
\textbf{Flow:}
\begin{enumerate}
    \item Fill in review metrics
    \item System stores evaluations
\end{enumerate}

\subsection*{UC10: Timetable Generation}
\textbf{Actors:} Admin \\
\textbf{Goal:} Create class timetables \\
\textbf{Flow:}
\begin{enumerate}
    \item Define structure and assign slots
    \item Publish for stakeholders
\end{enumerate}

\subsection*{UC11: Subject Allocation}
\textbf{Actors:} Admin \\
\textbf{Goal:} Link subjects to classes/teachers \\
\textbf{Flow:}
\begin{enumerate}
    \item Admin allocates and confirms
\end{enumerate}

\subsection*{UC12: Classroom Allocation}
\textbf{Actors:} Admin \\
\textbf{Goal:} Assign rooms for classes \\
\textbf{Flow:}
\begin{enumerate}
    \item Assign room, check for conflicts
    \item Save allocation
\end{enumerate}

\subsection*{UC13: Exam Schedule}
\textbf{Actors:} Admin \\
\textbf{Goal:} Set exam timetable \\
\textbf{Flow:}
\begin{enumerate}
    \item Enter exam dates
    \item Publish schedule
\end{enumerate}

\subsection*{UC14: Grading}
\textbf{Actors:} Teacher \\
\textbf{Goal:} Enter grades \\
\textbf{Flow:}
\begin{enumerate}
    \item Submit marks per subject
    \item System validates and stores
\end{enumerate}

\subsection*{UC15: Report Cards}
\textbf{Actors:} Admin / Teacher \\
\textbf{Goal:} Generate report cards \\
\textbf{Flow:}
\begin{enumerate}
    \item Compile grades/attendance
    \item Export and notify stakeholders
\end{enumerate}

\subsection*{UC16: Role-Based Access}
\textbf{Actors:} Admin \\
\textbf{Goal:} Manage system roles \\
\textbf{Flow:}
\begin{enumerate}
    \item Assign/update user roles
    \item Permissions updated in system
\end{enumerate}

\section{Non-Functional Requirements}
\begin{itemize}
    \item Usability: Intuitive for all users.
    \item Scalability: Supports growth.
    \item Performance: Responsive under load.
    \item Security: Encrypted, role-based access.
    \item Availability: High uptime.
\end{itemize}

\section{Stakeholder Expectations}
\begin{itemize}
    \item \textbf{Students:} Easy access to info.
    \item \textbf{Teachers:} Streamlined class tools.
    \item \textbf{Parents:} Timely updates.
    \item \textbf{Admins:} Full system control.
\end{itemize}

\section{System Goals}
\begin{itemize}
    \item Reduce paperwork.
    \item Increase transparency.
    \item Improve operations.
\end{itemize}

\section{System Architecture}
\begin{itemize}
    \item Web-based interface
    \item Cloud-hosted backend
    \item Modular components
\end{itemize}

\section{Technologies to Use}
\begin{itemize}
    \item Frontend: HTML5, CSS3, React/Angular
    \item Backend: Node.js / Django / Laravel
    \item Database: PostgreSQL / MongoDB
    \item Authentication: OAuth 2.0 / JWT
    \item Hosting: AWS / Azure / GCP
\end{itemize}

\section{Implementation Plan}
\begin{itemize}
    \item Phase 1: Requirement Gathering
    \item Phase 2: UI/UX Design
    \item Phase 3: Core Development
    \item Phase 4: Integration \& Testing
    \item Phase 5: Deployment \& Training
    \item Phase 6: Feedback Loop
\end{itemize}

\section{Conclusion}
This document outlines the functional and non-functional aspects of Bobby’s School System. With stakeholder-focused design and robust architecture, it aims to modernize school management effectively.

\end{document}
